Rao-Blackwellized smoother for Conditionally Linear and Gaussian models

### 2016-11-15 TexArxiv/clgm.tex
MAJ intro

More recently, \cite{lindsten:bunch:sarkka:schon:godsill:2015,sarkka:bunch:godsill:2012,lindsten:bunch:godsill:schon:2013} introduced a Rao Blackwellised smoother based on the forward-backward decomposition of the FFBS algorithm with Rao Blackwellisation steps both in the forward and backward time directions.
%The backward pass samples trajectories of indicator variables backward in time using the particles and weights of the forward pass.

@@

The paper is organized as follows. The proposed modification of the fully Rao Blackwellised Monte Carlo smoothers are presented in Section~\ref{sec:RaoBlackwell}. The performance of all these methods is illustrated in Section~\ref{sec:numerical:experiments} with simulated data. In Section~\ref{sec:crudeoil}, an application of regime switchings for commodity markets is presented using CME crude oil (WTI) data. A detailed derivation of the algorithms is provided in the Appendix.

>>>>

More recently, \cite{lindsten:bunch:sarkka:schon:godsill:2015,sarkka:bunch:godsill:2012,lindsten:bunch:godsill:schon:2013} introduced a Rao Blackwellised smoother based on the forward-backward decomposition of the FFBS algorithm with Rao Blackwellisation steps both in the forward and backward time directions. The update of the smoothing distribution of the regime given the observation shares some striking similarities with the Rauch-Tung-Striebel smoothing procedure, which is at the heart of the FFBS procedure. The Rao-Blackwellisation requires to update backward in time the smoothing distribution of the states given the regimes and the observations, which is achieved by using a \emph{à la Kalman} backward update.
%The backward pass samples trajectories of indicator variables backward in time using the particles and weights of the forward pass.

@@

The paper is organized as follows. The proposed modification of the fully Rao Blackwellised Monte Carlo smoothers are presented in Section~\ref{sec:RaoBlackwell}. The performance of all these methods is illustrated in Section~\ref{sec:numerical:experiments} with simulated data. In Section~\ref{sec:crudeoil}, an application to commodity markets is presented; the performance of our procedure is illustrated on crude oil  data. A detailed derivation of the algorithms is provided in the Appendix.
